---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# clessnverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/clessn/clessnverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/clessn/clessnverse/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

clessnverse contains functions for data domestication, analysis and visualization along with functions specific to the research chair's projects.

*Note: This package is under construction.*

## Installation

To install the latest stable version of this package, run the following line in your R console:

```R
remotes::install_github("clessn/clessnverse")
```

## Usage

`library("clessnverse")` will load the following packages:

- [hublot](https://github.com/clessn/hublotr), to access clHub
- [clessnhub](https://github.com/clessn/hublotr), to access clessn hub

## Examples

### Wrangle data

Normalize a continuous variable between 0 and 1

```{r example}
library(clessnverse)

data <- tibble::tibble(a = c(1, 0, 2, 0), b = c(4, 0, 1, 0))

# Base R
sapply(data, normalize_min_max)

# Dplyr
library("dplyr")

data %>%
  mutate(across(c(a, b), normalize_min_max))
```

### Visualise data

```{r}

p  <- ggplot2::ggplot(data = ggplot2::mpg) +
  ggplot2::geom_point(mapping = ggplot2::aes(x = displ, y = cty, colour = class)) +
  ggplot2::labs(title = "Look at this graph!",
                subtitle = "What a great theme, eh?",
                caption = "Data: API Twitter \nCLESSN") +
  ggplot2::xlab("x axis label") +
  ggplot2::ylab("y axis label")

p + theme_clean_light()
p + theme_clean_dark()

p  <- ggplot2::ggplot(data = ggplot2::mpg) +
  ggplot2::geom_point(mapping = ggplot2::aes(x = displ, y = cty, colour = class)) +
  ggplot2::labs(title = "Look at this graph!",
                subtitle = "What a great look, eh?",
                caption = "Data: Twitter API \nCLESSN")

p + scale_discrete_quorum(aesthetics = "colour")
```

## Issues and suggestions

You can submit bugs or suggestions in the Issues tab of this repo. To facilitate problem solving, please include a [minimal reproducible example](https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html) of the issue.
