---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clessnverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/clessn/clessnverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/clessn/clessnverse/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

clessnverse contains functions for data domestication, analysis and visualization along with functions specific to the research chair's projects.

*Note: This package is under construction.*

## Installation

To install the latest stable version of this package, run the following line in your R console:

```R
remotes::install_github("clessn/clessnverse")
```

## Usage

`library("clessnverse")` will load the following packages:

- [hublot](https://github.com/clessn/hublotr), to access clHub
- [clessnhub](https://github.com/clessn/hublotr), to access clessn hub

## Issues and suggestions

You can submit bugs or suggestions in the Issues tab of this repo. To facilitate problem solving, please include a [minimal reproducible example](https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html) of the issue.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(clessnverse)
## basic example code
```
